---
title: "Script utilizado en la charla"
output: false
---

`````markdown

---
title: "CV de Harry Potter"
author:
  firstname: Harry
  lastname: Potter
  address: "En algún lado"
  position: "Analista de datos ・ Profesor"
  contacts:
    - icon: fa envelope
      text: hp@gmail.com
      url: "mailto:ahp@gmail.com"
    - icon: assets/icon/bi-house-fill.svg
      text: miportfolio.com
      url: https://miportfolio.com
    - icon: fa brands orcid
      text: 0000-0000-0000-0000
      url: https://orcid.org/0000-0000-0000-0000
    - icon: fa brands github
      text: GitHub
      url: https://github.com/harrypotter
    - icon: fa brands linkedin
      text: LinkedIn
      url: https://linkedin.com/in/harrypotter
    - icon: fa brands x-twitter
      text: twitter
      url: https://twitter.com/poterh
format: awesomecv-typst
brand:
  typography: 
    fonts:
      - family: Roboto
        source: google
        weight: [100, 400, 700]
      - family: Source Sans 3
        source: google
        weight: [100, 400, 700]
        style: [normal, italic]
    base: Source Sans 3
  color:
    primary: "#fd8e73"
    link: "#771822"
  defaults: 
    awesomecv-typst:
      font-header: Roboto
execute: 
  echo: false
  warning: false
  output: false
---

## Educación

```{r}
#| output: asis

library(typstcv)
library(tidyverse)

df_cv <- readxl::read_excel('harry_potter_cv_es.xlsx') |> 
  mutate(start = as_date(start),
end = as_date(end)) |> 
  drop_na(start)

df_cv |> 
  filter(section == 'educacion') |>
  format_date(end = "end", sort_by = "start") |>
  resume_entry(title = "role",
               description = "institution",
               details = "descripcion")

```

## Experiencia laboral

```{r}
#| output: asis
df_cv |>
  filter(section == 'experiencia_laboral') |> 
  format_date(end = "end",
   sort_by = "start",
  date_format = "%Y",
  sep = "->",
    ) |>
  typstcv::resume_entry(title = "role",
               description = "institution")
```

## Experiencia Docente

```{r}
#| output: asis

df_cv |>
  filter(section == 'experiencia_docente') |> 
  format_date(end = "end",
   sort_by = "start",
  date_format = "%Y",
  sep = "->",
    ) |>
  typstcv::resume_entry(title = "role",
               description = "institution",
               details = c("description"),
               location = "location")
```

## Investigación

```{r}
#| output: asis

df_cv |> 
  filter(section == 'investigacion')|>
  format_date(end = "end", sort_by = "start") |>
  resume_entry(title = "role",
               description = "project",
               location = "institution",
               details = "description",
               date = "start") 
```
`````